Constructing a Convolutional Neural Network from ground up

### 2023-05-31 doc/paper.tex
Theory part almost completed
Signed-off-by: Gregz9 <gregorkajda@gmail.com>

\end{document}

>>>>

\subsection{Note}
All the theoretical concepts discussed, as well as the corresponding code for each component described, including the convolutional layer, pooling layer, and the CNN itself, are presented in a comprehensive Jupyter Notebook file here: \href{https://github.com/EricEReber/CNN/blob/main/doc/CNN_in_Python.ipynb}{\color{blue}CNN\ in\ Python}. The notebook provides detailed explanations and examples on how to use these components to build a fully functioning CNN. It serves as a valuable resource for understanding and implementing convolutional neural networks.
\end{document}
